\documentclass[9pt]{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[usenames]{color}
\usepackage{hyperref}

\leftmargin=0.25in
\oddsidemargin=0.25in
\textwidth=6.0in
\topmargin=-0.25in
\textheight=9.25in

\raggedright

\pagenumbering{arabic}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=black,
}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }
% DEFINITIONS FOR RESUME

\newenvironment{changemargin}[2]{%
  \begin{list}{}{%
    \setlength{\topsep}{0pt}%
    \setlength{\leftmargin}{#1}%
    \setlength{\rightmargin}{#2}%
    \setlength{\listparindent}{\parindent}%
    \setlength{\itemindent}{\parindent}%
    \setlength{\parsep}{\parskip}%
  }%
  \item[]}{\end{list}
}

\newcommand{\lineover}{
    \begin{changemargin}{-0.05in}{-0.05in}
        \vspace*{-8pt}
        \hrulefill \\
        \vspace*{-2pt}
    \end{changemargin}
}

\newcommand{\header}[1]{
    \begin{changemargin}{-0.5in}{-0.5in}
        \scshape{#1}\\
    \lineover
    \end{changemargin}
}

\newcommand{\contact}[4]{
    \begin{changemargin}{-0.5in}{-0.5in}
        \begin{center}
            {\Large \scshape {#1}}\\ \smallskip
            {#2}\\ \smallskip
            {#3}\\ \smallskip
            {#4}\smallskip
        \end{center}
    \end{changemargin}
}

\newenvironment{body} {
    \vspace*{-16pt}
    \begin{changemargin}{-0.25in}{-0.5in}
  }
    {\end{changemargin}
}

\newcommand{\school}[4]{
    \textbf{#1} \hfill \emph{#2\\}
    #3\\
    #4\\
}

% END RESUME DEFINITIONS

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Name
\contact{Saurabh Bajaj}{saurabhbsd@gmail.com}{+91-8000888022}{https://saurabhbajaj.dev}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Objective
\header{Summary}

\begin{body}
    \vspace{14pt}
  I am an experienced iOS application engineer currently working in Pune, India. I like to come up with simple solutions to difficult problems. Code quality, maintainability and pragmatism are my core programming principles. Being an iOS engineer, I give great attention to the UX and UI of the project.

\end{body}

\smallskip


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education
\header{Education}

\begin{body}
    \vspace{14pt}
    \textbf{Master in Computer Applications}{} \hfill \emph{Aug 2013 - Apr 2015}{} \\
    \emph{University of Pune}, Pune{} \\
\end{body}

\begin{body}
    \vspace{14pt}
    \textbf{Bachelor in Computer Applications}{} \hfill \emph{July 2010 - Apr 2013}{} \\
    \emph{University of Pune}, Pune{} \\
\end{body}

\smallskip


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education
\header{Certifications}

\begin{body}
    \vspace{14pt}
    \textbf{Diploma in iOS Application Development}{} \hfill \emph{June 2014 - Aug 2014}{} \\
    \emph{Sourcekode Technologies}, Pune{} \\
\end{body}

\smallskip


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Experience
\header{Career History}

\begin{body}
    \vspace{14pt}
    \textbf{Tech Lead - iOS}, \emph{Harman, Pune} \hfill \emph{Apr 2021 - Present}\\
    \begin{itemize} \itemsep -0pt  % reduce space between items
        \item Enriching the product application with new features and enhancements.
    \end{itemize}
    \begin{itemize} \itemsep -0pt  % reduce space between items
        \item Collaborate with the team to optimize existing features.
    \end{itemize}
    
    \vspace{14pt}
    \textbf{Team Lead - iOS}, \emph{Sell.do, Pune} \hfill \emph{Sept 2018 - Apr 2021}\\
    \begin{itemize} \itemsep -0pt  % reduce space between items
        \item Enriching the product application with new features and enhancements.
    \end{itemize}
    \begin{itemize} \itemsep -0pt  % reduce space between items
        \item Managing resources and ensuring timely development and delivery of application with minimal bugs.
    \end{itemize}
    \begin{itemize} \itemsep -0pt  % reduce space between items
        \item Interact with sales and support team for gathering requirements and collecting feedbacks from clients.
    \end{itemize}
    \vspace*{-4pt}

    \vspace{14pt}
    \textbf{iOS Developer}, \emph{Promobi Technologies, Pune} \hfill \emph{Nov 2015 - Sept 2018}\\
    \begin{itemize} \itemsep -0pt  % reduce space between items
        \item Own the complete product life-cycle from architecting to implementation and App Store release management.
    \end{itemize}
    \begin{itemize} \itemsep -0pt  % reduce space between items
        \item Worked on app performance optimisation by using profiling tools in Xcode.
    \end{itemize}
    \vspace*{-4pt}

    \vspace{14pt}
    \textbf{iOS Developer - Intern}, \emph{Emerson Innovation Center, Pune} \hfill \emph{Jan 2015 - Aug 2015}\\
    \vspace*{-4pt}
    \begin{itemize} \itemsep -0pt  % reduce space between items
        \item Worked on a Bluetooth based application in Objective-C.
    \end{itemize}

\end{body}

\smallskip

% \newpage{} % uncomment this line if you want to force a new page

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Apps
\header{Apps}

\begin{body}
    \vspace{14pt}
    \href{https://apps.apple.com/us/app/mobile-security-lookout/id434893913}{\textbf{Lookout:}}{} Data and Identity Protection tool. \\
    \vspace{2pt}
    \href{https://apps.apple.com/us/app/sell-do/id1225486345}{\textbf{Sell.Do:}}{} A CRM tool for real estate. \\
    \vspace*{2pt}
    \href{https://apps.apple.com/us/app/handwerkerstation/id1247972146}{\textbf{Handwerker Station:}}{} An ecommerce app. \\
    \vspace*{2pt}
    \href{https://apps.apple.com/us/app/brew-survey-offline-feedback/id1207197946}{\textbf{Brew Survey:}}{} A mobile survey and feedback solution. \\
    \vspace*{2pt}
    \href{https://itunes.apple.com/nz/app/booster-nz/id1179170506?mt=8}{\textbf{Booster:}}{} A snapshot of your finances at your fingertips. \\
    \vspace*{2pt}
    \href{https://itunes.apple.com/in/app/naki-laundry/id621934237?mt=8}{\textbf{Naki:}}{} An innovative tech based laundry service. \\
\end{body}

\newpage{}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Skills
\header{Skills}

\begin{body}
    \vspace{14pt}
    \emph{\textbf{Programming Languages:}}{} Swift, SwiftUI, Objective-C, C++, C, Python(minor experience)\\
    \vspace*{2pt}
    \emph{\textbf{Database:}}{} SQLite\\
    \vspace*{2pt}
    \emph{\textbf{Version Control:}}{} Git\\
    \vspace*{2pt}
    \emph{\textbf{Libraries and Frameworks:}}{} Cocoa Touch, AVFoundation, CoreData, CoreBluetooth, Map kit,
Firebase, Fabric \\
\vspace*{2pt}
    \emph{\textbf{Mobile Development:}}{} Native iOS Development \\
    \vspace*{2pt}
    \emph{\textbf{Operating Systems:}}{} macOS, Windows\\
\end{body}

\smallskip
\smallskip
\smallskip
\smallskip


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Links
\header{Important links}

\begin{body}
    \vspace{14pt}
    \textbf{Github} : https://github.com/saurabhbajajcode \hfill{}\\
    \smallskip
    \textbf{Linkedin} : https://www.linkedin.com/in/saurabhbajajcode/ \hfill{}\\
    \smallskip
    \textbf{Twitter} : https://twitter.com/saurabhbajaj91 \hfill{}\\
\end{body}

\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Leadership
\header{Achievements and Volunteering Experience}

\begin{body}
    \vspace{14pt}
    \textbf{Spotlight award in the Innovate category} : Internal award from Sell.do office\\
    \smallskip
    \textbf{Volunteer, City Level Walkathon} : Green Run, Lohgaon, Pune \hfill{} \emph{Dec 2019}\\
    \smallskip
    \textbf{Volunteer, National level Conference} : Sinhgad Institute of Management and Computer Applications, (Pune) \hfill {} \emph{Feb 2015}\\
\end{body}

\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Publications
% \header{Blog}

% \begin{body}
%     \vspace{14pt}
%     Gotchacode \textbf{Tech-blog covering topics related to web and Open Source.} \emph{ https://gotchacode.com}\\
%     \smallskip
% \end{body}

\smallskip

\end{document}
